Working title: Ecological network control

### 2018-05-19 paper/manuscript.Rmd
Improve matching explanation

Maximum matching is a widely studied topic in graph theory and is commonly used in multiple applications, ranging from dating apps and wireless communications to organ transplant allocation and peer to peer file sharing. 
A matching in an unweighted directed graph is defined as a set of links that do not share a common start or end nodes; the largest possible matching is called maximum matching. 
For example, in a network composed by jobs and job applicants, a matching is any pairing between applicants and positions that satisfies the basic constrain of any applicant being assigned to at most one position and visceversa.
A maximum matching would then be such a pairing that maximises the number of applicants with jobs and the number of positions filled. 
The definition of maximum matching, however, offer little insight about how it is related to structural controllability. 
The key is to note that the conditions of structural controllability imply that there needs to be a one to one relationship between *superior* and *subordinate* nodes (Figure \@ref(fig:fig-example-networks)b, bottom left). 
We use the maximum matching algorithm to pair superior to subordinate nodes in a way consistent with these conditions. 
The result is that a matching can actually be decomposed into a set of paths that reveal how a control signal can flow across the links in a network to reach every node that compose it. 
And so, as recently shown [@liu_controllability_2011], the minimum driver node set, those to which an external control signal should be applied to make the system controllable, corresponds exactly to the *unmatched* nodes in the network (Figure \@ref(fig:fig-control-configuration)).

>>>>

Maximum matching is a widely studied topic in graph theory and is commonly used in multiple applications, ranging from dating apps and wireless communications to organ transplant allocation and peer to peer file sharing. 
A matching in an unweighted directed graph is defined as a set of links that do not share a common start or end nodes; the largest possible matching is called maximum matching. 
For example, in a network composed by jobs and job applicants, a matching is any pairing between applicants and positions that satisfies one basic constrain: an applicant can be assigned to at most one position and visceversa.
Consequently, a maximum matching is an optimal pairing, one that maximises the number of applicants with jobs and the number of positions filled. 
At first glance, however, is  hard to identify how exactlty matchings are related to structural controllability. 
The key is to note that the conditions of structural controllability imply that, just like the one to one relationship between jobs and applicants, there needs to be a one to one relationship between *superior* and *subordinate* nodes (Figure \@ref(fig:fig-example-networks)b, bottom left). 
We use the maximum matching algorithm to find an optimal pairing of superior and subordinate nodes in a way consistent with the controllability conditions. 
The result is that a matching can actually be decomposed into a set of paths that reveal how a control signal can flow across the links in a network to reach every node that compose it. 
And so, as recently shown [@liu_controllability_2011], the minimum driver node set, those to which an external control input should be applied to make the system controllable, corresponds exactly to the *unmatched* nodes in the network (Figure \@ref(fig:fig-control-configuration)).
